A novel 1000\,\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers

### 2018-01-26 article.tex
1添加了用分析公式表 2添加了新旧系统热力学参数对比表，表格调成左对齐模式

\begin{table}[htbp]
\caption{The main input parameter of reference system }
\label{tab:ref input}
\centering
\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
 Live steam mass flow rate 	    	&t/h 			&2533 \\
 Live steam pressure 		    	&bar 			&310\\
 Live steam temperature		     	&$^\circ$C		&600		\\
 First reheat steam pressure    	&bar			&100.9		\\
 First reheat steam temperature  	&$^\circ$C		&610		\\
 Second reheat steam pressure    	&bar			&30.8		\\
 Second reheat steam temperature 	&$^\circ$C		&610		\\
 Power generation output 			&MW				&1000		\\
\bottomrule
\end{tabular}	
\end{table}
Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW. The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
\begin{table}[htbp]
\caption{fluid parameters of heat exchangers and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{cccc}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{2.7cm}{Cold fluid temperature($^\circ$C)}&  \multirow{2}{2.5cm}{LMTD($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

@@

\subsubsection{System analysis method} %(fold)
\label{ssub3:analsys method} 
%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
Usually, exergy loss and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
The general exergy balance of component can be expressed in the following form:
\begin{equation}
\label{equation:1}
\dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
\end{equation}
Exergy efficiency can be calculated in the following form:
\begin{equation}
\label{equation:2}
\eta=\frac{\dot{E}{}_{earned}}{\dot{E}{}_{cost}}
\end{equation}
For different equipment under stable operating conditions, equation~\ref{equation:1}~\ref{equation:2} have different forms as shown in Table 5~\cite{}
For flue gas, air, water and steam, the specific exergy can be calculated by equation~\ref{equation:3}.

\begin{equation}{}
\label{equation:3}
e=h-h_{0}-T_{0}\left(s-s_{0}\right)
\end{equation}
Then the total exergy rate associated with ﬂuid stream becomes:
\begin{equation}
\dot{E}=\dot{m}e=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
\end{equation}
The fuel speciﬁc exergy is calculated as[?]: 
\begin{equation}
e_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
\end{equation}
Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
\begin{table}
\caption{The exergy destruction rate and exergy efficiency equations for plant
components}
\label{table:exergy equation}
\centering{}%
\begin{tabular}{ccc}
\toprule {}
 & Exergy destruction rate & Exergy efficiency\tabularnewline
\midrule
Boiler &  & \tabularnewline
Pumps &  & \tabularnewline
Heaters &  & \tabularnewline
Turbine &  & \tabularnewline
Condenser &  & \tabularnewline
Cycle &  & \tabularnewline
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp]
\caption{The main input parameter of reference system }
\label{tab:ref input}
\centering
\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
 Live steam mass flow rate 	    	&t/h 			&2533 \\
 Live steam pressure 		    	&bar 			&310\\
 Live steam temperature		     	&$^\circ$C		&600		\\
 First reheat steam pressure    	&bar			&100.9		\\
 First reheat steam temperature  	&$^\circ$C		&610		\\
 Second reheat steam pressure    	&bar			&30.8		\\
 Second reheat steam temperature 	&$^\circ$C		&610		\\
 Power generation output 			&MW				&1000		\\
\bottomrule
\end{tabular}	
\end{table}
Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW. The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
\begin{table}[htbp]
\caption{fluid parameters of heat exchangers and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{llll}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{2.7cm}{Cold fluid temperature($^\circ$C)}&  \multirow{2}{2.5cm}{LMTD($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

@@

\subsubsection{System analysis method} %(fold)
\label{ssub3:analsys method} 
%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
Usually, exergy loss and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
The general exergy balance of component can be expressed in the following form:
\begin{equation}
\label{equation:1}
\dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
\end{equation}
Exergy efficiency can be calculated in the following form:
\begin{equation}
\label{equation:2}
\eta=\frac{\dot{E}{}_{earned}}{\dot{E}{}_{cost}}
\end{equation}
For different equipment under stable operating conditions, equation~\ref{equation:1}~\ref{equation:2} have different forms as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}
For flue gas, air, water and steam, the specific exergy can be calculated by equation~\ref{equation:3}.

\begin{equation}{}
\label{equation:3}
e=h-h_{0}-T_{0}\left(s-s_{0}\right)
\end{equation}
Then the total exergy rate associated with ﬂuid stream becomes:
\begin{equation}
\dot{E}=\dot{m}e=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
\end{equation}
The fuel speciﬁc exergy is calculated as[?]: 
\begin{equation}
e_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
\end{equation}
Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
\begin{table}
\caption{Exergy analysis equations for plant components}
\label{tab:exergy equation}
\centering
\begin{tabular}{lll}
\toprule 
 & Exergy destruction rate  & Exergy efficiency\tabularnewline
\midrule
Boiler & $\dot{I}_{boiler}=\dot{E}{}_{fuel}+\dot{E}{}_{in}-\dot{E}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{E}{}_{out}-\dot{E}{}_{in}}{\dot{E}{}_{fuel}}$\tabularnewline
Pump & $\dot{I}_{pump}=\dot{E}{}_{in}-\dot{E}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
Heater & $\dot{I}_{heater}=\dot{E}{}_{in}-\dot{E}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{E}{}_{in}}$\tabularnewline
Turbine & $\dot{I}_{turbine}=\dot{E}{}_{in}-\dot{E}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{E}{}_{in}-\dot{E}{}_{out}}$\tabularnewline
Condenser & $\dot{I}_{condenser}=\dot{E}{}_{in}-\dot{E}{}_{out}+\dot{W}{}_{p}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{E}{}_{out}}{\dot{E}{}_{in}+\dot{W}{}_{p}}$\tabularnewline
Cycle & $\dot{I}_{cycle}=\sum_{all}\dot{I}_{i}$ & $\eta_{\uppercase\expandafter{\romannumeral2},cycle}=\frac{\dot{W}{}_{net,out}}{\dot{E}{}_{fuel}}$\tabularnewline
\bottomrule
\end{tabular}
\end{table}

\subsection{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low. Using turbine extractions to heat air can realize the reduce the heat transfer temperature difference and improve efficiency. The economizer outlet flue gas is used to heat low-temperature economizer can also reduce the loss of regenerative system.
% In order to complete the heat balance calculation of the thermodynamic system, the key parameters in the novel system need to be set.
% The novel system’s parameters are based on reference system, so the main parameters must be the same. The main parameters settled are including: superheat steam’s mass flow, pressure and temperature; First/second reheater’s inlet and outlet pressure and temperature; Turbine Exhaust pressure and temperature; turbine extraction’s pressure and temperature/ specific enthalpy etc. The main parameters settled under THA situation can be found in Table 1 and Table 4 . 
The results of exergy analysis of the optimization system are presented in Table 5. It is found that the optimization system has an improvement in exergetic performance. The total exergy loss of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. The new system also brings the improvement from 46.98\% to 47.99\%. Results show that the exergy loss of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%. In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser. For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.

\begin{table}
\caption{Thermodynamic performance of the reference and novel systems}
\label{table:thermal performance compare}
\centering
\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
\toprule 
Items & Reference system & Novel system\tabularnewline
\midrule
Net generating power (MW) & 999.10 & 1011.19\tabularnewline
Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
Addition in generating efficiency (\%) &  & 1.04\tabularnewline
Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
Addition in generating efficiency (\%) &  & 1.01\tabularnewline
\bottomrule
\end{tabular}
\end{table}

% subsubsection subsubsection_name (end)
